%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Long Professional Curriculum Vitae
% LaTeX Template
% Version 1.1 (9/12/12)
%
% This template has been downloaded from:
% http://www.latextemplates.com
% Original author:
% Rensselaer Polytechnic Institute (http://www.rpi.edu/dept/arc/training/latex/resumes/)
%
% Important note:
% This template requires the res.cls file to be in the same directory as the
% .tex file. The res.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\let\latexnofiles\nofiles
\let\nofiles\relax
\documentclass[10pt]{res} % Use the res.cls style, the font size can be changed to 11pt or 12pt here

\usepackage{helvet} % Default font is the helvetica postscript font
%\usepackage{newcent} % To change the default font to the new century schoolbook postscript font uncomment this line and comment the one above
\usepackage{etaremune}
\usepackage{hyperref}

\newsectionwidth{0pt} % Stops section indenting

% Name shortcuts
\newcommand*\me[0]{{\bf Williams--Young,~D.~B.}}
\newcommand*\xsli[0]{Li,~X.}
\newcommand*\ko[0]{Ko,~J.}

\newcommand{\invited}{\item[$*$\theenumi.]}
%\newcommand{\invited}{\refstepcounter{enumi}\item[$*$\theenumi.]}

\begin{document}

%----------------------------------------------------------------------------------------
%	YOUR NAME AND ADDRESS(ES) SECTION
%----------------------------------------------------------------------------------------

\name{David Williams--Young\\ \\} % Your name at the top

% If you don't want one of the addresses, simply remove all the text in the first or second \address{} bracket

\address{{\bf Academic Address} \\ 
Department of Chemistry \\ 
University of Washington\\ 
311A Bagley Hall (office)\\
Box 351700 (mail)\\
Seattle, WA, USA 98195-1700\\
dbwy@u.washington.edu} % Your address 1

\address{{\bf Permanent Address} \\ 
1737 NW 56th St \\ 
Apt 504 \\
Seattle, WA, USA 98107 \\ 
+1 (248) 245-1211} % Your address 2

%----------------------------------------------------------------------------------------

\begin{resume}

%----------------------------------------------------------------------------------------
%	OBJECTIVE SECTION
%----------------------------------------------------------------------------------------

\section{\centerline{OBJECTIVE}}

\vspace{8pt} % Gap between title and text

To obtain a research position relating to chemical theory and computation.


%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{\centerline{EDUCATION}} 

\vspace{8pt} % Gap between title and text

{\sl Doctor of Philosophy (Pursuant)}, Chemistry \hfill (Projected) May 2018 \\ 
University of Washington, Seattle, WA   \\ 
Adviser: Dr. Xiaosong Li
 
{\sl Bachelor of Science (Magna Cum Laude)}, Chemistry, Mathematics \hfill May 2013  \\ 
Indiana University of Pennsylvania, Indiana, PA \\
Adviser: Dr. Jaeju Ko

%----------------------------------------------------------------------------------------
 
%----------------------------------------------------------------------------------------
%	PROFESSIONAL EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{\centerline{PROFESSIONAL EXPERIENCE}} 

\vspace{8pt} % Gap between title and text

{\sl Graduate Research Assistant} \hfill July 2013 -- Present \\
University of Washington, Seattle, WA

{\sl Graduate Teaching Assistant} \hfill September 2013 -- Present \\
University of Washington, Seattle, WA 

{\sl Undergraduate Research Assistant} \hfill September 2011 -- May 2013 \\
Indiana University of Pennsylvania, Indiana, PA

{\sl Chemistry Tutor} \hfill August 2010 -- May 2011 \\
Indiana University of Pennsylvania Disability Services, Indiana, PA 

%----------------------------------------------------------------------------------------



%----------------------------------------------------------------------------------------
%	PUBLICATIONS SECTION
%----------------------------------------------------------------------------------------

\section{\centerline{PUBLICATIONS}} 
\vspace{-2pt} % Gap between title and text
\begin{center}
{\bf 4 in press publications, 2 as first author}\\

* Indicates equal contribution to published work 
\end{center}

\begin{etaremune}
  \item Van Beeuman, R.; \me; Kasper, J.; Yang, C.; Ng, E. G.; \xsli;
        ``\emph{A Model Order Reduction Algorithm for Estimating the 
	        Absorption Spectrum}"
        \textbf{2017}, In Preparation.
  \item \me; Scalmani, G.; Sun, S.; Frisch, M.; \xsli;
        ``\emph{On the Accurate and Efficient Evaluation of the 
	        Analytical Hessians of Electronically Excited States 
		within the Random Phase Approximation}"
        \textbf{2017}, In Preparation.
  \item \me; Hongbin Liu; \xsli;
        ``\emph{Time--Dependent Density Functional Theory (TD-DFT) Benchmark
	        of Excited--State Polarizabilities}"
        \textbf{2017}, In Preparation.
  \item Egidi, F.*; \me*; Baiardi, A.*; Bloino, J.; Scalmani, G.; Frisch, M.; 
        \xsli; Barone, V.; 
        ``\emph{Effective Inclusion of Mechanical and Electrical Anharmonicity in 
                Excited Electronic States: the VPT2-TDDFT Route}"
          \emph{J. Chem. Theor. Comp.}, \textbf{2017}, Submitted.
  \item Petrone,~A.*; \me*; Lingerfelt,~D.~B.; \xsli;
        ``\emph{Ab Initio Transient Raman Analysis}"
	  \emph{J. Phys. Chem. A.}, \textbf{2017}, Submitted.
  \item \me*; Lingerfelt, D.~B.*; Petrone, A.; \xsli;
	``\emph{Ab Initio Surface Hopping Dynamics within the Particle-Particle 
	        Tamm--Dancoff Approximation}"
          \emph{J. Chem. Phys. Comm.}, \textbf{2017}, \emph{Submitted}.
  \item Petrone,~A.; Lingerfelt,~D.~B.; \me; \xsli;
        ``\emph{Ab Initio Transient Vibrational Spectral Analysis}"
	  \emph{J. Phys. Chem. Lett.}, \textbf{2016}, 7, 4501--4508.
  \item \me; Goings,~J.; \xsli;
	``\emph{Accelerating Real--Time Time-Dependent Density Functional Theory 
	        with a Non--Recursive Chebyshev Expansion of the Quantum 
                Propagator}"
	  \emph{J. Chem. Theor. Comp.}, \textbf{2016}, 12(11) 5333--5338.
  \item \me; Egidi,~F.; \xsli;
	``\emph{Relativistic Two-Component Particle-Particle Tamm--Dancoff 
	        Approximation}"
	  \emph{J. Chem. Theor. Comp.}, \textbf{2016}, 12(11), 5379--5384.
  \item Lingerfelt,~D.~B.; \me; Petrone,~A; \xsli; 
        ``\emph{Direct ab Initio (Meta-)Surface-Hopping Dynamics}", 
        \emph{J. Chem. Theor. Comp.}, \textbf{2016}, 12(3), 935--945.
\end{etaremune}
%  Papers that are on hold for now:
%
%  \item \me*; Lingerfelt, D.~B.*; Petrone, A.; \xsli;
%	``\emph{Ab Initio Surface Hopping Dynamics within the Particle-Particle 
%	        Tamm--Dancoff Approximation}"
%          \emph{J. Chem. Phys. Comm.}, \textbf{2016}, \emph{Submitted}.
%\begin{center}
%*Authors contributed equally to this work
%\end{center}


\section{\centerline{CURRENT SOFTWARE CITATIONS}} 
\vspace{15pt} % Gap between title and text

\begin{etaremune}
  \item \xsli; Valeev,~E.~F.; \me; Ding,~F.; Liu,~H.; Goings,~J.~J.; Petrone,~A.; Lestrange,~P.;
        \emph{Chronus Quantum, Beta Version}, \url{http://www.chronusquantum.org}, \textbf{2016}.

\item Frisch,~M.~J.; Trucks,~G.~W.; Schlegel,~H.~B.; Scuseria,~G.~E.; Robb,~M.~A.;
      Cheeseman,~J.~R.; Scalmani,~G.; Barone,~V.; Petersson,~G.~A.; Nakatsuji,~H.; \xsli;
      Caricato,~M.; Marenich,~A.; Bloino,~J.; Janesko,~B.~G.; Gomperts,~R.; Mennucci,~B.;
      Hratchian,~H.~P.; Izmaylov,~A.~F.; Sonnenberg,~J.~L.; \me; Ding,~F.; Lipparini,~F.;
      Egidi,~F.; Goings,~J.; Peng,~B.; Petrone,~A.; Ortiz,~J.~V.; Zakrzewski,~V.~G.; Gao,~J.;
      Rega,~N.; Zheng,~G.; Liang,~W.; Hada,~M.; Ehara,~M.; Toyota,~K.; Fukuda,~R.; Hasegawa,~J.;
      Ishida,~M.; Nakajima,~T.; Honda,~Y.; Kitao,~O.; Nakai,~H.; Vreven,~T.; Throssell,~K.; Montgomery~Jr.,~J.~A.;
      Peralta,~J.~E.; Ogliaro,~F.; Bearpark,~M.; Heyd,~J.~J.; Brothers,~E.; Kudin,~K.~N.; Staroverov,~V.~N.; Keith,~T.;
      Kobayashi,~R.; Normand,~J.; Raghavachari,~K.; Rendell,~A.; Burant,~J.~C.; Iyengar,~S.~S.;
      Tomasi,~J.; Cossi,~M.; Millam,~J.~M.; Klene,~M.; Adamo,~C.; Cammi,~R.;
      Ochterski,~J.~W.; Martin,~R.~L.; Morokuma,~K.; Farkas,~O.; Foresman,~J.~B.; and Fox~,~D.~J.;
      \emph{Gaussian 16, A.03},
      Gaussian, Inc., Wallingford CT, \textbf{2016}.
\end{etaremune}

\vspace{0.2in} % Some whitespace between sections
%----------------------------------------------------------------------------------------
%	HONORS SECTION
%----------------------------------------------------------------------------------------

\section{\centerline{HONORS}} 

\vspace{-5pt} % Reduce space between section title and contents

\begin{center}
Nicole A. Boand Endowed Fellowship in Chemistry \hfill ARCS Foundation (2016) \\
Early Bird Research Assistantship (EBRA) \hfill University of Washington (2013) \\
Excellence in Chemistry Graduate Fellowship Award (ECGFA) \hfill University of Washington (2013)\\
Provost Scholar \hfill Indiana University of Pennsylvania (2013)
\end{center}

%----------------------------------------------------------------------------------------
%	MEMBERSHIPS SECTION
%----------------------------------------------------------------------------------------

\section{\centerline{MEMBERSHIPS}} 

\vspace{-5pt} % Reduce space between section title and contents

\begin{center}
Alpha Chi Sigma ($\mathrm{AX}\Sigma$), $\Gamma\mathrm{T}$ Chapter, Professional Chemistry Fraternity\\
American Chemical Society (ACS), Computers in Chemistry Division
\end{center}

%----------------------------------------------------------------------------------------

\end{resume} 
\end{document}
